---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# 0. ggnorthcarolina

## Installation

You can install the development version of ggnorthcarolina from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggnorthcarolina")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggnorthcarolina)

northcarolina_flat %>% head()

library(ggplot2)
northcarolina_flat %>%
ggplot() +
  aes(fips = FIPS) +
  geom_sf_countynorthcarolina() ->
A

last_plot() + 
  aes(fill = BIR74) ->
B

library(patchwork)
A + B

northcarolina_flat %>%
ggplot() +
aes(fips = FIPS, 
    fill = SID74,
    label = paste0(NAME, "\n", SID74)) +
  geom_sf_countynorthcarolina() +
  geom_label_northcarolina_county(
    lineheight = .7,
    size = 2, 
    check_overlap= TRUE,
    color = "oldlace")
```




<!-- badges: start -->
<!-- badges: end -->

# 1. The second-order goal of ggnorthcarolina is to serve as a model and template for other ggplot-based geography-specific convenience mapping packages. 

Let's look at the package contents

```{r}
fs::dir_tree(recurse = F)
```

The data-raw and R folder are where all the creative action happens.

```{r}
fs::dir_tree(path = "data-raw", recurse = F)
fs::dir_tree(path = "R", recurse = F)
```

# A. Prepare reference datasets

The functions that you create in the R folder will use data that is prepared in the ./data-raw/DATASET.R file.  Let's have a look at the contents of that file to get a sense of the preparation.

## ./data-raw/DATASET.R

```{r, code = readLines("./data-raw/DATASET.R"), eval=FALSE}


```

The prepared data is documented in ./R/data.R


## ./R/data.R

```{r, code = readLines("./R/data.R"), eval=FALSE}


```

# B. Prepare functions for building polygons defined by ids

## ./R/geom.R

```{r, code = readLines("./R/geom.R"), eval=FALSE}

```

## ./R/stamp.R

```{r, code = readLines("./R/stamp.R"), eval=FALSE}

```


## ./R/labels.R

```{r, code = readLines("./R/labels.R"), eval=FALSE}

```
